%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mo Shan (Sean)} \\ \vspace{1pt}
    \small moshan@ucsd.edu $|$
    \href{https://moshan.cf}{\underline{http://moshan.cf/}} $|$ 
    \href{https://www.linkedin.com/in/mo-shan-21393452/}{\underline{https://www.linkedin.com/in/mo-shan}} $|$
    \href{https://github.com/shanmo}{\underline{https://github.com/shanmo}} $|$ 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    % \resumeSubheading
    %   {University of California, San Diego}{La Jolla, CA, USA}
    %   {PhD in Electrical and Computer Engineering, \textit{GPA 3.74/4}}{Expected Jun. 2022}
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA, USA}
      {Master of Science in Electrical and Computer Engineering, \textit{GPA 3.74/4}}
      {Sept. 2016 -- Dec. 2019}
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Bachelor of Science in Electrical and Computer Engineering, \textit{GPA 4.84/5}}
      {Sept. 2010 -- Jun. 2014}
    \resumeSubheading
      {University of Southampton}{Southampton, United Kingdom}
      {Student Exchange Program in School of Electronics and Computer Science}
      {Dec. 2012 -- Jul. 2013}
  \resumeSubHeadingListEnd


%-----------Research Interests-----------
% \section{Research Interests}
%   \resumeSubHeadingListStart
%       \resumeSubItem
      
% \resumeItemListStart
% \resumeSubHeadingListEnd

%   \resumeItemListStart
%   \resumeItem{Rich models of tightly coupled localization and environmental representation that unify multiple characteristics, such as the geometric landmarks, semantic object-level map, object surfaces, and yet scale to large environments in real-time on embedded platforms such as quadrotors}
%   \resumeItem{Simultaneous localization and mapping; visual-inertial odometry}
%   \resumeItem{Relevant fields: computer vision, machine learning, optimization}
%   \resumeItemListEnd
  
%   \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Intern}{Jun. 2021 -- Sept. 2021}
      {\textsc{Facebook Reality Labs}}{USA}
      \resumeItemListStart
        \resumeItem{Worked remotely on a project related to AR/VR and delivered results with a high impact}
        \resumeItem{Used modern C++, Python, PyTorch}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{Jun. 2018 -- Jun. 2021}
      {\textsc{ECE, UCSD}}{USA}
      \resumeItemListStart
        \resumeItem{Designed and developed a tightly coupled, filtering based semantic VIO (OrcVIO) that produces an object-level map, with C++, Python, OpenCV, Sophus, Eigen, PyTorch}
        \resumeItem{OrcVIO is $4.8\%$ better in object mapping accuracy compared with a single view object mapping approach, and $23.4\%$ better in localization accuracy compared with an object SLAM approach, on the KITTI dataset}
      \resumeItemListEnd

    \resumeSubheading
      {Associate Scientist}{Jun. 2014 -- Sept. 2016}
      {\textsc{Temasek Laboratories}}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed a Google Map aided visual odometry with C++, OpenCV, Dlib, which increases the localization accuracy by $96.0\%$ compared with the baseline}
        \resumeItem{Implemented an UAV navigation approach based on a laser-stereo sensor suite with C++, OpenCV}
      \resumeItemListEnd

    \resumeSubheading
      {Summer Intern}{Jun. 2012 -- Sept. 2012}
      {\textsc{Infineon}}{Singapore}
      \resumeItemListStart
        % \resumeItem{Evaluated the performance of the AC-HMI-OLED prototype card}
        % \resumeItem{Performed quality test of the Class D amplifier, Infrared Receiver and the Boost Converter}
        \resumeItem{Tested features such as a-law compression, volume control, Manchester decoding and voltage conversion}
        \resumeItem{Developed a Simulink model for touch sensing, and performed real time noise filtering}
    \resumeItemListEnd

    \resumeSubheading
      {Summer Intern}{Jun. 2011 -- Sept. 2011}
      {\textsc{Interactive Digital Media Institute}}{Singapore}
      \resumeItemListStart
        \resumeItem{Implemented a foreground detection algorithm based on RPCA using MATLAB, reaching more than $70\%$ precision at recall higher than $90\%$, which outperforms state-of-the-art}
        \resumeItem{Designed and developed a painting classification algorithm using sparse coding with MATLAB, achieving $2.3$ times better authentication accuracy than the baseline}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Information Technology Support Specialist}{Sep. 2018 -- Present}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Communicate with managers to set up campus computers used on campus}
    %     \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
    %     \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    % \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd
  

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++ 11/14/17, MATLAB} \\
     \textbf{Frameworks}{: ROS} \\
     \textbf{Developer Tools}{: Vim, Git, Docker, VS Code, PyCharm} \\
     \textbf{Libraries}{: OpenCV, Dlib, scikit-image $\|$ Eigen, Sophus $\|$ PyTorch, Tensorflow, Keras}
    }}
 \end{itemize}

  
%-----------Awards-----------
\section{Awards}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Multi-Year Dean$'$s Fellowship and Jacobs Fellowship}{Sept. 2016 -- Sept. 2017}
      {\textsc{UCSD}}{La Jolla, CA, USA}
      \resumeItemListStart
        \resumeItem{Most prestigious fellowship offered by the ECE Department}
      \resumeItemListEnd

    \resumeSubheading
      {The 3rd International UAV Innovation Grand Prix}{Nov. 2015}
      {AVIC}{Zhejiang, China}
      \resumeItemListStart
        \resumeItem{Championship of rotary wing competition with a monetary prize of 100,000 RMB}
        \resumeItem{Designed and implemented a bucket detection algorithm to guide bucket transfer for the firefighting task using a UAV, with C++, OpenCV and Dlib}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd



%-----------Professional Activities-----------
\section{Professional Activities}
  \resumeSubHeadingListStart
  
  \resumeItem{\textbf{Teaching Assistant}}
      \resumeItemListStart
        \resumeItem{ECE 276A: Sensing $\&$ Estimation in Robotics (Winter Quarter, 2021)}
        \resumeItem{Class size: 80. Duties include answering questions related to lecture notes, grading the homework and projects, and designing a project on VI SLAM.)}
        \resumeItem{For the students who provided evaluation, 75.0\% says "Strongly Agree" when asked "I would recommend this Instructional Assistant to other students.".}
    \resumeItemListEnd
  
  \resumeItem{\textbf{Talks}}
      \resumeItemListStart
        \resumeItem{\textit{ELLIPSDF: Joint Object Pose and Shape Optimization with a Bi-level Ellipsoid and Signed Distance Function Description}, ICCV Poster Presentation, Oct. 11, 2021.}
        \resumeItem{\textit{OrcVIO: Object residual constrained Visual-Inertial Odometry}, IROS Oral Presentation, Oct. 25, 2020.}
        \resumeItem{\textit{Geo-referenced UAV Localization}, Paopao Robot Open-course, April 21, 2018.}
    \resumeItemListEnd
  
  \resumeItem{\textbf{Reviewer}}
      \resumeItemListStart
        \resumeItem{Journals: IEEE Transactions on Robotics (T-RO), IEEE Robotics and Automation Letters (RA-L), International Journal of Computer Vision (IJCV)}
        \resumeItem{Conferences: IEEE International Conference on Robotics and Automation (ICRA), IEEE International Conference on Intelligent Robots and Systems (IROS), IEEE International Conference on Computer Vision and Pattern Recognition (CVPR)}
    \resumeItemListEnd
    
  \resumeItem{\textbf{Successful Grant Proposals}}
      \resumeItemListStart
        \resumeItem{NSF research grant. \textit{Lyapunov-Certified Cognitive Control for Safe
Autonomous Navigation in Unknown Environments}. (2017). Principal investigator: Prof. Nikolay Atanasov.}
        \resumeItem{Temasek Laboratories research grant for seed projects. \textit{Laser-aided Stereo Vision for UAV Navigation}. (2015). Principal investigator: Mo Shan.}
    \resumeItemListEnd
    
\resumeItem{\textbf{Membership}}
    \resumeItemListStart
     \resumeItem{IEEE Student Member}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	One Page 
%----------------------------------------------------------------------------------------

%-----------Selected publications-----------
\section{Selected Publications}
  \resumeSubHeadingListStart
  
  \resumeItem{\textbf{Journal Articles}}
      \resumeItemListStart
        \resumeItem{\textbf{M. Shan}, V. Dhiman, Q. Feng, J. Li, N. Atanasov. “OrcVIO: Object residual constrained Visual-Inertial Odometry”. (2021). arXiv:2007.15107. Submitted to IEEE Transactions on Robotics (T-RO).}
        \resumeItem{Z. Gao, \textbf{M. Shan}, Q. Li. (2015). Adaptive Sparse Representation for Analyzing Artistic Style of Paintings. ACM Journal on Computing and Cultural Heritage.}
        \resumeItem{Z. Gao, Q. Li., R. Zhai, \textbf{M. Shan}, F. Lin. (2015). Adaptive and Robust Sparse Coding for Laser Range Data Denoising and Inpainting. IEEE Transactions on Circuits and Systems for Video Technology.}
    \resumeItemListEnd
    
  \resumeItem{\textbf{Conference Proceedings}}
      \resumeItemListStart
        \resumeItem{\textbf{M. Shan}, Q. Feng, Y. Jau, N. Atanasov. (2021). “ELLIPSDF: Joint Object Pose and Shape Optimization with a Bi-level Ellipsoid and Signed Distance Function Description”. In IEEE International Conference on Computer Vision (ICCV). Montreal, Canada. \textbf{25.9\% acceptance rate}.}
        \resumeItem{\textbf{M. Shan}, Q. Feng, N. Atanasov. (2020). OrcVIO: Object residual constrained Visual-Inertial Odometry. In IEEE International Conference on Intelligent Robots and Systems (IROS). Las Vegas, USA. \textbf{47\% acceptance rate}.}
        \resumeItem{Q. Feng, Y. Meng, \textbf{M. Shan}, N. Atanasov. (2019). Localization and Mapping using Instance-specific Mesh Models. In IEEE International Conference on Intelligent Robots and Systems (IROS). Macao, China.}
        \resumeItem{\textbf{M. Shan}, Y. Bi, H. Qin, J. Li, Z. Gao, F. Lin and B. M. Chen. (2016). A brief survey of visual odometry for micro aerial vehicles, Proceedings of the 42nd Annual Industrial Electronics Conference (IECON), Florence, Italy.}
        \resumeItem{\textbf{M. Shan}, Fei Wang, Feng Lin, Zhi Gao, Ya Z. Tang, Ben M. Chen. (2015). Google Map Aided Visual Navigation for UAVs in GPS-denied Environment. In IEEE International Conference on Robotics and Biomimetics (ROBIO). Zhuhai, China.}
        \resumeItem{Z. Gao, \textbf{M. Shan}, L. Cheong, Q. Li. (2014). Adaptive Sparse Coding for Painting Style Analysis. In Computer Vision-ACCV 2014. Springer Berlin Heidelberg.}
        \resumeItem{Z. Gao, L. Cheong, \textbf{M. Shan}. (2012). Block-sparse rpca for consistent foreground detection. In Computer Vision-ECCV 2012 (pp. 690-703). Springer Berlin Heidelberg.}
    \resumeItemListEnd
    
  \resumeItem{\textbf{Workshop Papers}}
      \resumeItemListStart
        \resumeItem{\textbf{M. Shan}. (2019). Weakly supervised keypoint detection. Southern California Robotics Symposium (SCR), Pasadena, USA.}
        \resumeItem{\textbf{M. Shan}, N. Atanasov. (2017). A spatiotemporal model with visual attention for video classification. In Robotics: Science and Systems (RSS) Workshop on Articulated Model Tracking, Cambridge, USA.}
        \resumeItem{\textbf{M. Shan}, A. Charan. (2015). Google Map Referenced UAV Navigation via Simultaneous Feature Detection and Description. Poster paper. In IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS). Hamburg, Germany.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
